\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-12 introduction.tex
use \paragraph

Meanwhile, language designers and researchers are increasingly
using proof assistants to mechanize meta\-theories, building on each
other's work.
Therefore, it has become ever more important that proof assistants
make it easy to write reusable, extensible code and proofs.

\large{\textbf{Structure of the paper}} We will quickly introduce Family Polymorphism and the challenges to adapt it into dependent type setting in \cref{sec:background+challenge}. After that, we will talk about the language design of family polymorphism in dependent type setting and the implementation of our Coq plugin in \cref{sec:coqimpl}. Then, we consider the meta-theory of incorporating family polymorphism into predicative MLTT, and deriving consistency and canonicity results in \cref{sec:metatheory}. \ref{sec:related-work} discusses related works and \ref{sec:conclusion} concludes.

\large{\textbf{Contributions}} include the following
\begin{itemize}
  \item To our knowledge, this is the first attempt incorporating family polymorphism with theorem proving and higher order logic
  \item We contribute a prototypical Coq plugin for the interested users and developers 
  \item We provide some first-step meta-theoretical results, including consistency and canonicity
\end{itemize}

>>>>

Meanwhile, language designers and researchers are increasingly
using proof assistants to mechanize meta\-theories, building on each
other's work.
As a result, it has become ever more important that proof assistants
make it easy to write reusable, extensible code and proofs.

\paragraph{Structure of the paper} 
We will quickly introduce Family Polymorphism and the challenges to adapt it into dependent type setting in \cref{sec:background+challenge}. After that, we will talk about the language design of family polymorphism in dependent type setting and the implementation of our Coq plugin in \cref{sec:coqimpl}. Then, we consider the meta-theory of incorporating family polymorphism into predicative MLTT, and deriving consistency and canonicity results in \cref{sec:metatheory}. \ref{sec:related-work} discusses related works and \ref{sec:conclusion} concludes.

\paragraph{Contributions} include the following
\begin{itemize}
  \item To our knowledge, this is the first attempt incorporating family polymorphism with theorem proving and higher order logic
  \item We contribute a prototypical Coq plugin for the interested users and developers 
  \item We provide some first-step meta-theoretical results, including consistency and canonicity
\end{itemize}
